Cards model analysis

### 2020-04-22 cards_model_analysis.Rmd
Basic meta-learning plot + CIs

>>>>

## Basic meta-learning plot
```{r}
theme_set(theme_classic())
```

```{r}
summarized_loss_d = loss_d %>%
  filter(run_type == "exact_eval",
         !meta) %>%
  group_by(run, epoch, train_or_eval) %>%
  summarize(loss = mean(loss, na.rm=T) / 0.53)
```

```{r}
ggplot(summarized_loss_d,
       aes(x=epoch, y=loss, color=train_or_eval)) +
  geom_line(aes(group=interaction(run, train_or_eval)),
            alpha=0.2) +
  geom_line(stat="summary",
            fun.y="mean",
            size=1) +
  scale_color_manual(breaks=c("train", "eval"), 
                     labels=c("Trained\ngames", "Held-out\ngames"),
                     values=c("#4d9221", "#c51b7d")) +
  labs(y="Average meta-learning rewards\n(% of optimal)", x="Epoch") +
  scale_y_continuous(breaks=c(0, 0.5, 1), labels=c("0%", "50%", "100%")) +
  guides(color=guide_legend(title=NULL)) +
  theme(legend.position=c(0.8, 0.25),
        legend.key.size = unit(1.5, "lines"))

ggsave("../metamapping_paper/figures/basic_meta_learning_cards.png", width=4, height=3)
ggsave("../../psych/dissertation/3-human-adaptation/figures/basic_meta_learning_cards.png", width=5, height=3)
```

```{r}
set.seed(0)  # reproducibility
summarized_loss_d %>%
  filter(epoch %in% c(0, 5000)) %>%
  group_by(train_or_eval, epoch) %>%
  do(results=mean_cl_boot(.$loss, na.rm=T)) %>%
  mutate(mean=results$y,
         CIlow=results$ymin,
         CIhigh=results$ymax)
```
